Measuring Individual Partisan Harm in Redistricting

### 2021-09-03 paper/paper.Rmd
reforming intro

Understanding fairness in electoral systems has long suffered from a focus on parties over the individuals who vote for them.
There is no doubt that parties are interesting units in electoral discussions.
They offer stability over candidates, information for the under-informed, and shortcuts for understanding preferred vote choices.
Yet, court histories and academic traditions value the harm of the individual over the harm to a transient political body, such as the party.

@@

    -   Recent advances allow us to make claims about harm based in counterfactuals that are realistic and statistically useful

## Running Examples

>>>>

What is the question?

Districting is a complicated process.
Residents of a state or locality must be partitioned into districts.
These districts must adhere to many constraints, often requiring components such as contiguity and equal population.
In drawing the districts, it's easy to lose sight of the individuals impacted by district drawing.
Often, we consider how parties succeed or fail under the electoral environments generated by enacted plans.
Yet this misses that parties are formed by voters who ally with parties.
Rather than considering parties, we ask how individuals are harmed or benefited by the districting process?

Why does it matter?

Why is it hard?
Decades of

What did we do?

What did we learn?

What is the paper's contribution?

```{=html}
<!--
Understanding fairness in electoral systems has long suffered from a focus on parties over the individuals who vote for them.
There is no doubt that parties are interesting units in electoral discussions.
They offer stability over candidates, information for the under-informed, and shortcuts for understanding preferred vote choices.
Yet, court histories and academic traditions value the harm of the individual over the harm to a transient political body, such as the party.

@@

    -   Recent advances allow us to make claims about harm based in counterfactuals that are realistic and statistically useful
-->
```
## Running Examples
